The SMT Competition 2015--2018

### 2019-08-21 2018/report/Reviews_67398_Revised_Response.txt

> * Rules
>
> - basically incorrect results are "ignored" by omitting the benchmark if the status is not known - this comment still remains. The authors updated the text. I see their points and analysis, which I appreciated, through I think that this is an issue that should be dealt with more care. Correctness is very important for solvers when checking in particular real benchmarks (HW- and SW-verification, etc).

DONE (updated to better motivate the removal of benchmarks with
disagreements; of course we agree that correctness is important)

> * Significance of the results
>
>  - the paper and its analysis now contain many numbers and data, which is very appropriate for e competition report in my opinion. But, basically, no explanation is in place. What I expect to get out of a report, other than commenting the numbers, is their explanation, e.g.: what are the techniques implemented in solvers that overall performed better? Rr better, what techniques implemented in solvers led to an efficient solvers on a particular benchmark? why such techniques led to positive results on benchmarks with (a) given structure/characteristics?

WONTFIX (while interesting, this is way out of scope for this paper:
we, as organizers, are not the developers of most of the solvers (nor
the source of most benchmarks), so there is no practical way for us to
determine what exactly was the cause for improvement)

@@

>  - "whose precise" ->  ", whose precise"

DONE

>  - "DT" looks not to be introduced

WONTFIX ("DT" for algebraic datatypes is introduced in Section 3)

### 2019-08-22 2018/report/SMT-COMP.tex
Move Scoring into its own section; minor

Complete data about past competitions since 2015 (and partly for
earlier competitions) is available from the competition website,
\url{http://www.smtcomp.org}.  This includes detailed results for each
solver/benchmark combination, totaling nearly 6 million data records
(about 1.1~GB in CSV format).  Competition solvers and benchmarks may
be downloaded from StarExec, \url{https://www.starexec.org}.

The rest of this paper is structured as follows.  In
Section~\ref{sec:goals}, we present the goals and organization of the
competition.  Section~\ref{sec:smtlib} introduces the SMT-LIB language
and library, and Section~\ref{sec:benchmarks} discusses competition
divisions and benchmarks.  The competition is being run on StarExec,
which is described in Section~\ref{sec:starexec}.
Section~\ref{sec:participants} gives an overview of participating
solvers.  Selected competition results are presented in
Section~\ref{sec:results}, and analyzed in more detail in
Section~\ref{sec:analysis}.  We conclude with suggestions for future
SMT Competitions in Section~\ref{sec:conclusions}.

@@

The 2018 release of the SMT Library contained \num{336844} non-incremental
benchmarks in 51 logics, as well as~\num{10167} incremental benchmarks
(with a total of nearly 32 million {\tt check-sat} commands) in 26
logics.  Table~\ref{table:smtlib} presents further data on the size of
the SMT Library since~2015.  While the library usually grows from one
year to the other because of the inclusion of new benchmarks and
logics, continuous curation efforts may also cause benchmarks to be
removed or reclassified on occasion, thereby causing individual logics
or even the entire library to shrink.  From~2015 to~2018, the total
number of benchmarks has increased by~68\,\%.  The largest benchmark
in the 2018 release had a size of \num{1041}~MB; the total size of the
release was 91~GB.

@@

\subsection{Scoring}

@@

@@

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2018.pdf}}
  \caption{VBS on common benchmarks 2015--2018 of all logics in the \maintrack
  with a time limit of 1200s. Number of common benchmarks is indicated with a
  gray vertical line.}
  \label{fig:progress-all}
\end{figure}

\begin{figure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2014-2015.pdf}}
    \caption{2014 vs.~2015}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2016.pdf}}
    \caption{2015 vs.~2016}
  \end{subfigure}
  \\[2ex]
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2016-2017.pdf}}
    \caption{2016 vs.~2017}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2017-2018.pdf}}
    \caption{2017 vs.~2018}
  \end{subfigure}
  \caption{VBS on common benchmarks for pairs of years of all logics in the
  \maintrack with a time limit of 1200s. Number of common benchmarks is
  indicated with a gray vertical line.}
  \label{fig:progress}
\end{figure}

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
  plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
  \vspace{-5ex}
  \caption{VBS in terms of correct \texttt{check-sat} answers
  (out of 30370517 total)
  within a time limit of 2400s
  on common benchmarks 2015--2018 of all logics in the \apptrack.}
  \label{fig:progress-all-app}
\end{figure}

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
  plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Unsat_Core_Track_2016-2018.pdf}}
  \vspace{-5ex}
  \caption{VBS in terms of number of unsat core reductions
  within a time limit of 2400s
  on common benchmarks 2016--2018 of all logics in the \ucoretrack.}
  \label{fig:progress-all-uc}
\end{figure}

>>>>

Complete data about past competitions since 2015 (and partly for
earlier competitions) is available from the competition website,
\url{http://www.smtcomp.org}.  This includes detailed results for each
solver/benchmark combination, totaling nearly 6 million data records
(about \SI{1.1}{GB} in CSV format).  Competition solvers and
benchmarks may be downloaded from StarExec,
\url{https://www.starexec.org}.

The rest of this paper is structured as follows.  In
Section~\ref{sec:goals}, we present the goals and organization of the
competition.  Section~\ref{sec:smtlib} introduces the SMT-LIB language
and library, and Section~\ref{sec:benchmarks} discusses competition
divisions and benchmarks.  The competition is being run on StarExec,
which is described in Section~\ref{sec:starexec}.
Section~\ref{sec:participants} gives an overview of participating
solvers, and Section~\ref{sec:scoring} discusses the scoring rules.
Selected competition results are presented in
Section~\ref{sec:results}, and analyzed in more detail in
Section~\ref{sec:analysis}.  We conclude with suggestions for future
SMT Competitions in Section~\ref{sec:conclusions}.

@@

The 2018 release of the SMT Library contained \num{336844}
non-incremental benchmarks in 51 logics, as well as~\num{10167}
incremental benchmarks (with a total of nearly 32 million {\tt
  check-sat} commands) in 26 logics.  Table~\ref{table:smtlib}
presents further data on the size of the SMT Library since~2015.
While the library usually grows from one year to the other because of
the inclusion of new benchmarks and logics, continuous curation
efforts may also cause benchmarks to be removed or reclassified on
occasion, thereby causing individual logics or even the entire library
to shrink.  From~2015 to~2018, the total number of benchmarks has
increased by~68\,\%.  The largest benchmark in the 2018 release had a
size of \SI{1041}{MB}; the total size of the release was \SI{91}{GB}.

@@

@@

\section{Scoring}
\label{sec:scoring}

@@

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2018.pdf}}
  \caption{VBS on common benchmarks 2015--2018 of all logics in the
    \maintrack with a time limit of \SI{1200}{s}.  Number of common
    benchmarks is indicated with a gray vertical line.}
  \label{fig:progress-all}
\end{figure}

\begin{figure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2014-2015.pdf}}
    \caption{2014 vs.~2015}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2016.pdf}}
    \caption{2015 vs.~2016}
  \end{subfigure}
  \\[2ex]
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2016-2017.pdf}}
    \caption{2016 vs.~2017}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2017-2018.pdf}}
    \caption{2017 vs.~2018}
  \end{subfigure}
  \caption{VBS on common benchmarks for pairs of years of all logics
    in the \maintrack with a time limit of \SI{1200}{s}.  Number of
    common benchmarks is indicated with a gray vertical line.}
  \label{fig:progress}
\end{figure}

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
  plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
  \vspace{-5ex}
  \caption{VBS in terms of correct \texttt{check-sat} answers (out of
    \num{30370517} total) within a time limit of \SI{2400}{s} on
    common benchmarks 2015--2018 of all logics in the \apptrack.}
  \label{fig:progress-all-app}
\end{figure}

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
  plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Unsat_Core_Track_2016-2018.pdf}}
  \vspace{-5ex}
  \caption{VBS in terms of number of unsat core reductions within a
    time limit of \SI{2400}{s} on common benchmarks 2016--2018 of all
    logics in the \ucoretrack.}
  \label{fig:progress-all-uc}
\end{figure}
